\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-20 doc/incertae_sedis.tex
correction to rank-based i.s.

As mentioned above, the \emph{incertae sedis} annotation may mean that a taxon is
unplaced, but only a few placements within the taxonomy are possible.
For example, a genus may not be characterized as incertae sedis at the
level of the subfamily.
Thus, it could be placed inside any of the
hypothesized sub-families, or within its own subfamily, but it would
be unexpected for it to be placed inside one of the other genera
within a family.

>>>>

As mentioned above, the \emph{incertae sedis} annotation may mean that a taxon is
unplaced, but only a few placements within the taxonomy are possible.
For example, a genus might be characterized as \emph{incertae sedis}
at the level of the subfamily.
Thus, it could be placed inside any of the
hypothesized sub-families, or within its own subfamily, but it would
be unexpected for it to be placed inside one of the other genera.
